Bx to Rev (tentative) \thanks{Supported by organization x.}

### 2019-08-23 paper/main.tex
Update main.tex

            \item For left-associative \& recursive composition (breverse):\\
            - all times should be non-linear (\textcolor{blue}{due to there is no linear number of function calls})
        \end{itemize}
    \item Memory allocation (MBytes)
        \begin{itemize}
            \item Memory usage depends on the input size and the number of composition
            \item In general, minbigul uses less memory than the others for non-recursive compositions (all tests except breverse)
            \item pg only uses memory efficient when handling right-associative composition 
            \item cpg \& kpg are worst in memory allocation for right-associative
            \item For left-associative \& recursive composition (breverse), minbigul uses significantly more memory than kpg as well as xpg.
        \end{itemize}
\end{itemize}

>>>>

            \item For left-associative \& recursive composition (breverse):\\
            - all times should be non-linear (\textcolor{blue}{because there is no linear number of function calls})
        \end{itemize}
    \item Memory allocation (MBytes)
        \begin{itemize}
            \item Memory usage depends on the input size and the number of composition
            \item In general, minbigul uses less memory than the others for non-recursive compositions (all tests except breverse)
            \item pg only uses memory efficient when handling right-associative composition 
            \item cpg \& kpg are worst in memory allocation for right-associative
            \item For left-associative \& recursive composition (breverse), minbigul uses significantly more memory than kpg as well as xpg.
        \end{itemize}
\end{itemize}
